### 2017-10-28 monograph/thesis/chapters/introduction.tex
Fixed fatal error due not escaping _ on introduction.tex

    \item Global identifiers must start with `g_' prefix.

@@

    \item Boolean variables must be prefix with `is_' even when they are in
    global scope, meaning double prefixed as `g_is_'.

@@

    Java programming language has no such idealism as exhaustively prefixing as
    `g_' as explicitly there is not such concept. Although a more hawk-eyed
    reader may spot about the Java classes atributes being the global variables.
    And in fact they are so. But within their scope limited to the classes body,
    and perhaps the instance objects which may or may not provide access to
    them.

>>>>

    \item Global identifiers must start with `g\_' prefix.

@@

    \item Boolean variables must be prefix with `is\_' even when they are in
    global scope, meaning double prefixed as `g\_is\_'.

@@

    Java programming language has no such idealism as exhaustively prefixing as
    `g\_' as explicitly there is not such concept. Although a more hawk-eyed
    reader may spot about the Java classes atributes being the global variables.
    And in fact they are so. But within their scope limited to the classes body,
    and perhaps the instance objects which may or may not provide access to
    them.
